Inverse energy transfer in three-dimensional quantum vortex flows

### 2025-03-05 arxiv-submission.tex
Added .bbl file to tex for arxiv submission

\bibliography{references}% Produces the bibliography via BibTeX

>>>>

% \bibliography{references}% Produces the bibliography via BibTeX

%apsrev4-2.bst 2019-01-14 (MD) hand-edited version of apsrev4-1.bst
%Control: key (0)
%Control: author (8) initials jnrlst
%Control: editor formatted (1) identically to author
%Control: production of article title (0) allowed
%Control: page (0) single
%Control: year (1) truncated
%Control: production of eprint (0) enabled
\begin{thebibliography}{61}%
    \makeatletter
    \providecommand \@ifxundefined [1]{%
     \@ifx{#1\undefined}
    }%
    \providecommand \@ifnum [1]{%
     \ifnum #1\expandafter \@firstoftwo
     \else \expandafter \@secondoftwo
     \fi
    }%
    \providecommand \@ifx [1]{%
     \ifx #1\expandafter \@firstoftwo
     \else \expandafter \@secondoftwo
     \fi
    }%
    \providecommand \natexlab [1]{#1}%
    \providecommand \enquote  [1]{``#1''}%
    \providecommand \bibnamefont  [1]{#1}%
    \providecommand \bibfnamefont [1]{#1}%
    \providecommand \citenamefont [1]{#1}%
    \providecommand \href@noop [0]{\@secondoftwo}%
    \providecommand \href [0]{\begingroup \@sanitize@url \@href}%
    \providecommand \@href[1]{\@@startlink{#1}\@@href}%
    \providecommand \@@href[1]{\endgroup#1\@@endlink}%
    \providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
      `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
    \providecommand \@@startlink[1]{}%
    \providecommand \@@endlink[0]{}%
    \providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
    \providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
    \providecommand \urlprefix  [0]{URL }%
    \providecommand \Eprint [0]{\href }%
    \providecommand \doibase [0]{https://doi.org/}%
    \providecommand \selectlanguage [0]{\@gobble}%
    \providecommand \bibinfo  [0]{\@secondoftwo}%
    \providecommand \bibfield  [0]{\@secondoftwo}%
    \providecommand \translation [1]{[#1]}%
    \providecommand \BibitemOpen [0]{}%
    \providecommand \bibitemStop [0]{}%
    \providecommand \bibitemNoStop [0]{.\EOS\space}%
    \providecommand \EOS [0]{\spacefactor3000\relax}%
    \providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
    \let\auto@bib@innerbib\@empty
    %</preamble>
    \bibitem [{\citenamefont {Frisch}(1995)}]{frisch1995}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {U.}~\bibnamefont
      {Frisch}},\ }\href@noop {} {\bibinfo {title} {\emph{Turbulence: {{The
      Legacy}} of {{A}}. {{N}}. {{Kolmogorov}}}}} (\bibinfo {year}
      {1995})\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Canuto}\ and\ \citenamefont
      {Christensen-Dalsgaard}(1998)}]{canuto-dalsgaard-1998}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.~M.}\ \bibnamefont
      {Canuto}}\ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
      {Christensen-Dalsgaard}},\ }\bibfield  {title} {\bibinfo {title} {Turbulence
      in astrophysics: stars},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
      {journal} {Ann. Rev. Fluid Mech.}\ }\textbf {\bibinfo {volume} {30}},\
      \bibinfo {pages} {167} (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Barenghi}\ \emph
      {et~al.}(2023{\natexlab{a}})\citenamefont {Barenghi}, \citenamefont
      {Middleton-Spencer}, \citenamefont {Galantucci},\ and\ \citenamefont
      {Parker}}]{barenghi-etal-2023}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~F.}\ \bibnamefont
      {Barenghi}}, \bibinfo {author} {\bibfnamefont {H.~A.~J.}\ \bibnamefont
      {Middleton-Spencer}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
      {Galantucci}},\ and\ \bibinfo {author} {\bibfnamefont {N.~G.}\ \bibnamefont
      {Parker}},\ }\bibfield  {title} {\bibinfo {title} {Types of quantum
      turbulence},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {AVS
      Quantum Sci.}\ }\textbf {\bibinfo {volume} {5}},\ \bibinfo {pages} {025601}
      (\bibinfo {year} {2023}{\natexlab{a}})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Barenghi}\ \emph
      {et~al.}(2023{\natexlab{b}})\citenamefont {Barenghi}, \citenamefont
      {Skrbek},\ and\ \citenamefont
      {Sreenivasan}}]{Barenghi_Skrbek_Sreenivasan_2023}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~F.}\ \bibnamefont
      {Barenghi}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Skrbek}},\
      and\ \bibinfo {author} {\bibfnamefont {K.~R.}\ \bibnamefont {Sreenivasan}},\
      }\href@noop {} {\emph {\bibinfo {title} {Quantum Turbulence}}}\ (\bibinfo
      {publisher} {Cambridge University Press},\ \bibinfo {year}
      {2023})\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Richardson}(1922)}]{richardson1922weather}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~F.}\ \bibnamefont
      {Richardson}},\ }\href@noop {} {\emph {\bibinfo {title} {{W}eather
      {P}rediction by {N}umerical {P}rocess}}}\ (\bibinfo  {publisher} {University
      Press},\ \bibinfo {year} {1922})\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Kolmogorov}(1941)}]{kolmogorov-1941}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
      {Kolmogorov}},\ }\bibfield  {title} {\bibinfo {title} {The local structure of
      turbulence in an incompressible viscous fluid for very large {{R}}eynolds
      numbers},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Dokl.
      Akad. Nauk. SSSR}\ }\textbf {\bibinfo {volume} {30}},\ \bibinfo {pages} {301}
      (\bibinfo {year} {1941})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Kraichnan}(1967)}]{kraichnan-1967}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
      {Kraichnan}},\ }\bibfield  {title} {\bibinfo {title} {Inertial ranges in
      two‐dimensional turbulence},\ }\href@noop {} {\bibfield  {journal}
      {\bibinfo  {journal} {Phys. Fluids}\ }\textbf {\bibinfo {volume} {10}},\
      \bibinfo {pages} {1417} (\bibinfo {year} {1967})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Boffetta}\ and\ \citenamefont
      {Ecke}(2012)}]{boffetta-ecke-2012}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
      {Boffetta}}\ and\ \bibinfo {author} {\bibfnamefont {R.~E.}\ \bibnamefont
      {Ecke}},\ }\bibfield  {title} {\bibinfo {title} {Two-dimensional
      turbulence},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Ann.
      Rev. Fluid Mech.}\ }\textbf {\bibinfo {volume} {44}},\ \bibinfo {pages} {427}
      (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Boffetta}\ and\ \citenamefont
      {Musacchio}(2010)}]{boffetta-musacchio-2010}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
      {Boffetta}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
      {Musacchio}},\ }\bibfield  {title} {\bibinfo {title} {Evidence for the double
      cascade scenario in two-dimensional turbulence},\ }\href
      {https://doi.org/10.1103/PhysRevE.82.016307} {\bibfield  {journal} {\bibinfo
      {journal} {Phys. Rev. E}\ }\textbf {\bibinfo {volume} {82}},\ \bibinfo
      {pages} {016307} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Laurie}\ \emph {et~al.}(2014)\citenamefont {Laurie},
      \citenamefont {Boffetta}, \citenamefont {Falkovich}, \citenamefont
      {Kolokolov},\ and\ \citenamefont {Lebedev}}]{laurie-etal-2014}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
      {Laurie}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Boffetta}},
      \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Falkovich}}, \bibinfo
      {author} {\bibfnamefont {I.}~\bibnamefont {Kolokolov}},\ and\ \bibinfo
      {author} {\bibfnamefont {V.}~\bibnamefont {Lebedev}},\ }\bibfield  {title}
      {\bibinfo {title} {Universal profile of the vortex condensate in
      two-dimensional turbulence},\ }\href
      {https://doi.org/10.1103/PhysRevLett.113.254503} {\bibfield  {journal}
      {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {113}},\
      \bibinfo {pages} {254503} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Tisza}(1938)}]{tisza-1938}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
      {Tisza}},\ }\bibfield  {title} {\bibinfo {title} {Transport phenomena in
      helium {{II}}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
      {Nature}\ }\textbf {\bibinfo {volume} {141}},\ \bibinfo {pages} {913}
      (\bibinfo {year} {1938})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Landau}(1949)}]{landau-1949}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
      {Landau}},\ }\bibfield  {title} {\bibinfo {title} {On the theory of
      superfluidity},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
      {Phys. Rev.}\ }\textbf {\bibinfo {volume} {75}},\ \bibinfo {pages} {884}
      (\bibinfo {year} {1949})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Skrbek}\ and\ \citenamefont
      {Sreenivasan}(2012)}]{skrbek-sreenivasan-2012}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
      {Skrbek}}\ and\ \bibinfo {author} {\bibfnamefont {K.~R.}\ \bibnamefont
      {Sreenivasan}},\ }\bibfield  {title} {\bibinfo {title} {Developed quantum
      turbulence and its decay},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
      {journal} {Phys. Fluids}\ }\textbf {\bibinfo {volume} {24}},\ \bibinfo
      {pages} {011301} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Jackson}\ \emph {et~al.}(2009)\citenamefont
      {Jackson}, \citenamefont {Proukakis}, \citenamefont {Barenghi},\ and\
      \citenamefont {Zaremba}}]{jackson-etal-2009}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
      {Jackson}}, \bibinfo {author} {\bibfnamefont {N.~P.}\ \bibnamefont
      {Proukakis}}, \bibinfo {author} {\bibfnamefont {C.~F.}\ \bibnamefont
      {Barenghi}},\ and\ \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
      {Zaremba}},\ }\bibfield  {title} {\bibinfo {title} {Finite-temperature vortex
      dynamics in bose-einstein condensates},\ }\href@noop {} {\bibfield  {journal}
      {\bibinfo  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume} {79}},\
      \bibinfo {pages} {053615} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Hall}\ and\ \citenamefont
      {Vinen}(1956{\natexlab{a}})}]{hall-vinen-1956a}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.~E.}\ \bibnamefont
      {Hall}}\ and\ \bibinfo {author} {\bibfnamefont {W.~F.}\ \bibnamefont
      {Vinen}},\ }\bibfield  {title} {\bibinfo {title} {The rotation of liquid
      helium~{{II}}. i. experiments on the propagation of secound sound in
      uniformly rotating helium {{II}}},\ }\href@noop {} {\bibfield  {journal}
      {\bibinfo  {journal} {Proc. R. Soc. London A}\ }\textbf {\bibinfo {volume}
      {238}},\ \bibinfo {pages} {204} (\bibinfo {year}
      {1956}{\natexlab{a}})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Hall}\ and\ \citenamefont
      {Vinen}(1956{\natexlab{b}})}]{hall-vinen-1956b}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.~E.}\ \bibnamefont
      {Hall}}\ and\ \bibinfo {author} {\bibfnamefont {W.~F.}\ \bibnamefont
      {Vinen}},\ }\bibfield  {title} {\bibinfo {title} {The rotation of liquid
      helium~{{II}}. ii. the theory of mutual friction in uniformly rotating helium
      {{II}}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Proc. R.
      Soc. London A}\ }\textbf {\bibinfo {volume} {238}},\ \bibinfo {pages} {215}
      (\bibinfo {year} {1956}{\natexlab{b}})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Maurer}\ and\ \citenamefont
      {Tabeling}(1998)}]{maurer1998}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
      {Maurer}}\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
      {Tabeling}},\ }\bibfield  {title} {\bibinfo {title} {Local investigation of
      superfluid turbulence},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
      {journal} {Europhys. Lett.}\ }\textbf {\bibinfo {volume} {43}},\ \bibinfo
      {pages} {29} (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Salort}\ \emph {et~al.}(2010)\citenamefont {Salort},
      \citenamefont {Baudet}, \citenamefont {Castaing}, \citenamefont {Chabaud},
      \citenamefont {Daviaud}, \citenamefont {Didelot}, \citenamefont {Diribarne},
      \citenamefont {Dubrulle}, \citenamefont {Gagne}, \citenamefont {Gauthier},
      \citenamefont {Girard}, \citenamefont {H\'ebral}, \citenamefont {B.},
      \citenamefont {Thibault},\ and\ \citenamefont {Roche}}]{salort2010turbulent}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
      {Salort}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Baudet}},
      \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Castaing}}, \bibinfo
      {author} {\bibfnamefont {B.}~\bibnamefont {Chabaud}}, \bibinfo {author}
      {\bibfnamefont {F.}~\bibnamefont {Daviaud}}, \bibinfo {author} {\bibfnamefont
      {T.}~\bibnamefont {Didelot}}, \bibinfo {author} {\bibfnamefont
      {P.}~\bibnamefont {Diribarne}}, \bibinfo {author} {\bibfnamefont
      {B.}~\bibnamefont {Dubrulle}}, \bibinfo {author} {\bibfnamefont
      {Y.}~\bibnamefont {Gagne}}, \bibinfo {author} {\bibfnamefont
      {F.}~\bibnamefont {Gauthier}}, \bibinfo {author} {\bibfnamefont
      {A.}~\bibnamefont {Girard}}, \bibinfo {author} {\bibfnamefont
      {B.}~\bibnamefont {H\'ebral}}, \bibinfo {author} {\bibfnamefont
      {R.}~\bibnamefont {B.}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
      {Thibault}},\ and\ \bibinfo {author} {\bibfnamefont {P.-E.}\ \bibnamefont
      {Roche}},\ }\bibfield  {title} {\bibinfo {title} {Turbulent velocity spectra
      in superfluid flows},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
      {journal} {Phys. Fluids}\ }\textbf {\bibinfo {volume} {22}} (\bibinfo {year}
      {2010})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Baggaley}\ \emph {et~al.}(2012)\citenamefont
      {Baggaley}, \citenamefont {Sherwin}, \citenamefont {Barenghi},\ and\
      \citenamefont {Sergeev}}]{baggaley2012}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~W.}\ \bibnamefont
      {Baggaley}}, \bibinfo {author} {\bibfnamefont {L.~K.}\ \bibnamefont
      {Sherwin}}, \bibinfo {author} {\bibfnamefont {C.~F.}\ \bibnamefont
      {Barenghi}},\ and\ \bibinfo {author} {\bibfnamefont {Y.~A.}\ \bibnamefont
      {Sergeev}},\ }\bibfield  {title} {\bibinfo {title} {Thermally and
      mechanically driven quantum turbulence in helium {{II}}},\ }\href@noop {}
      {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo
      {volume} {86}},\ \bibinfo {pages} {104501} (\bibinfo {year}
      {2012})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {{Sherwin-Robson}}\ \emph {et~al.}(2015)\citenamefont
      {{Sherwin-Robson}}, \citenamefont {Barenghi},\ and\ \citenamefont
      {Baggaley}}]{sherwin-robson2015}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~K.}\ \bibnamefont
      {{Sherwin-Robson}}}, \bibinfo {author} {\bibfnamefont {C.~F.}\ \bibnamefont
      {Barenghi}},\ and\ \bibinfo {author} {\bibfnamefont {A.~W.}\ \bibnamefont
      {Baggaley}},\ }\bibfield  {title} {\bibinfo {title} {Local and nonlocal
      dynamics in superfluid turbulence},\ }\href@noop {} {\bibfield  {journal}
      {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {91}},\
      \bibinfo {pages} {104517} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Müller}\ and\ \citenamefont
      {Krstulovic}(2020)}]{Muller_KolmogorovKelvinWave_2020}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~P.}\ \bibnamefont
      {Müller}}\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
      {Krstulovic}},\ }\bibfield  {title} {\bibinfo {title} {Kolmogorov and
      {Kelvin} wave cascades in a generalized model for quantum turbulence},\
      }\href {https://doi.org/10.1103/PhysRevB.102.134513} {\bibfield  {journal}
      {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
      {102}},\ \bibinfo {pages} {134513} (\bibinfo {year} {2020})}\BibitemShut
      {NoStop}%
    \bibitem [{\citenamefont {Müller}\ \emph {et~al.}(2021)\citenamefont
      {Müller}, \citenamefont {Polanco},\ and\ \citenamefont
      {Krstulovic}}]{Muller_IntermittencyVelocityCirculation_2021}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~P.}\ \bibnamefont
      {Müller}}, \bibinfo {author} {\bibfnamefont {J.~I.}\ \bibnamefont
      {Polanco}},\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
      {Krstulovic}},\ }\bibfield  {title} {\bibinfo {title} {Intermittency of
      {Velocity} {Circulation} in {Quantum} {Turbulence}},\ }\href
      {https://doi.org/10.1103/PhysRevX.11.011053} {\bibfield  {journal} {\bibinfo
      {journal} {Phys. Rev. X}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo
      {pages} {011053} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Middleton-Spencer}\ \emph {et~al.}(2022)\citenamefont
      {Middleton-Spencer}, \citenamefont {Orozco}, \citenamefont {Galantucci},
      \citenamefont {Moreno}, \citenamefont {Parker}, \citenamefont {Machado},
      \citenamefont {Bagnato},\ and\ \citenamefont
      {Barenghi}}]{middleton-spencer2022}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.~A.~J.}\
      \bibnamefont {Middleton-Spencer}}, \bibinfo {author} {\bibfnamefont
      {A.~D.~G.}\ \bibnamefont {Orozco}}, \bibinfo {author} {\bibfnamefont
      {L.}~\bibnamefont {Galantucci}}, \bibinfo {author} {\bibfnamefont
      {M.}~\bibnamefont {Moreno}}, \bibinfo {author} {\bibfnamefont {N.~G.}\
      \bibnamefont {Parker}}, \bibinfo {author} {\bibfnamefont {L.~A.}\
      \bibnamefont {Machado}}, \bibinfo {author} {\bibfnamefont {V.~S.}\
      \bibnamefont {Bagnato}},\ and\ \bibinfo {author} {\bibfnamefont {C.~F.}\
      \bibnamefont {Barenghi}},\ }\bibfield  {title} {\bibinfo {title} {Evidence of
      strong quantum turbulence in {{B}}ose-{{E}}instein condensates},\ }\href@noop
      {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Research}\ }\textbf
      {\bibinfo {volume} {5}},\ \bibinfo {pages} {043081} (\bibinfo {year}
      {2022})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Bradley}\ and\ \citenamefont
      {Anderson}(2012)}]{bradley2012energy}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~S.}\ \bibnamefont
      {Bradley}}\ and\ \bibinfo {author} {\bibfnamefont {B.~P.}\ \bibnamefont
      {Anderson}},\ }\bibfield  {title} {\bibinfo {title} {Energy spectra of vortex
      distributions in two-dimensional quantum turbulence},\ }\href@noop {}
      {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\ }\textbf {\bibinfo
      {volume} {2}},\ \bibinfo {pages} {041001} (\bibinfo {year}
      {2012})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Reeves}\ \emph {et~al.}(2013)\citenamefont {Reeves},
      \citenamefont {Billam}, \citenamefont {Anderson},\ and\ \citenamefont
      {Bradley}}]{reeves2013}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~T.}\ \bibnamefont
      {Reeves}}, \bibinfo {author} {\bibfnamefont {T.~P.}\ \bibnamefont {Billam}},
      \bibinfo {author} {\bibfnamefont {B.~P.}\ \bibnamefont {Anderson}},\ and\
      \bibinfo {author} {\bibfnamefont {A.~S.}\ \bibnamefont {Bradley}},\
      }\bibfield  {title} {\bibinfo {title} {Inverse energy cascade in forced
      two-dimensional quantum turbulence},\ }\href@noop {} {\bibfield  {journal}
      {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {110}},\
      \bibinfo {pages} {104501} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Simula}\ \emph {et~al.}(2014)\citenamefont {Simula},
      \citenamefont {Davis},\ and\ \citenamefont
      {Helmerson}}]{simula2014emergence}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
      {Simula}}, \bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont {Davis}},\
      and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Helmerson}},\
      }\bibfield  {title} {\bibinfo {title} {Emergence of order from turbulence in
      an isolated planar superfluid},\ }\href
      {https://doi.org/10.1103/PhysRevLett.113.165302} {\bibfield  {journal}
      {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {113}},\
      \bibinfo {pages} {165302} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Müller}\ and\ \citenamefont
      {Krstulovic}(2024)}]{Muller_ExploringEquivalenceTwoDimensional_2024}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~P.}\ \bibnamefont
      {Müller}}\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
      {Krstulovic}},\ }\bibfield  {title} {\bibinfo {title} {Exploring the
      {Equivalence} between {Two}-{Dimensional} {Classical} and {Quantum}
      {Turbulence} through {Velocity} {Circulation} {Statistics}},\ }\href
      {https://doi.org/10.1103/PhysRevLett.132.094002} {\bibfield  {journal}
      {\bibinfo  {journal} {Phys. Rev. Letters}\ }\textbf {\bibinfo {volume}
      {132}},\ \bibinfo {pages} {094002} (\bibinfo {year} {2024})}\BibitemShut
      {NoStop}%
    \bibitem [{\citenamefont {Johnstone}\ \emph {et~al.}(2019)\citenamefont
      {Johnstone}, \citenamefont {Groszek}, \citenamefont {Starkey}, \citenamefont
      {Billington}, \citenamefont {Simula},\ and\ \citenamefont
      {Helmerson}}]{johnstone2019evolution}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~P.}\ \bibnamefont
      {Johnstone}}, \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont
      {Groszek}}, \bibinfo {author} {\bibfnamefont {P.~T.}\ \bibnamefont
      {Starkey}}, \bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont
      {Billington}}, \bibinfo {author} {\bibfnamefont {T.~P.}\ \bibnamefont
      {Simula}},\ and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
      {Helmerson}},\ }\bibfield  {title} {\bibinfo {title} {Evolution of
      large-scale flow from turbulence in a two-dimensional superfluid},\
      }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf
      {\bibinfo {volume} {364}},\ \bibinfo {pages} {1267} (\bibinfo {year}
      {2019})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Gauthier}\ \emph {et~al.}(2019)\citenamefont
      {Gauthier}, \citenamefont {Reeves}, \citenamefont {Yu}, \citenamefont
      {Bradley}, \citenamefont {Baker}, \citenamefont {Bell}, \citenamefont
      {Rubinsztein-Dunlop}, \citenamefont {Davis},\ and\ \citenamefont
      {Neely}}]{gauthier2019giant}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
      {Gauthier}}, \bibinfo {author} {\bibfnamefont {M.~T.}\ \bibnamefont
      {Reeves}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Yu}}, \bibinfo
      {author} {\bibfnamefont {A.~S.}\ \bibnamefont {Bradley}}, \bibinfo {author}
      {\bibfnamefont {M.~A.}\ \bibnamefont {Baker}}, \bibinfo {author}
      {\bibfnamefont {T.~A.}\ \bibnamefont {Bell}}, \bibinfo {author}
      {\bibfnamefont {H.}~\bibnamefont {Rubinsztein-Dunlop}}, \bibinfo {author}
      {\bibfnamefont {M.~J.}\ \bibnamefont {Davis}},\ and\ \bibinfo {author}
      {\bibfnamefont {T.~W.}\ \bibnamefont {Neely}},\ }\bibfield  {title} {\bibinfo
      {title} {Giant vortex clusters in a two-dimensional quantum fluid},\
      }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf
      {\bibinfo {volume} {364}},\ \bibinfo {pages} {1264} (\bibinfo {year}
      {2019})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Fj{\o}rtoft}(1953)}]{fjortoft1953changes}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
      {Fj{\o}rtoft}},\ }\bibfield  {title} {\bibinfo {title} {On the changes in the
      spectral distribution of kinetic energy for twodimensional, nondivergent
      flow},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Tellus}\
      }\textbf {\bibinfo {volume} {5}},\ \bibinfo {pages} {225} (\bibinfo {year}
      {1953})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Zhu}\ \emph {et~al.}(2023)\citenamefont {Zhu},
      \citenamefont {Semisalov}, \citenamefont {Krstulovic},\ and\ \citenamefont
      {Nazarenko}}]{Zhu_DirectInverseCascades_2023}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
      {Zhu}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Semisalov}},
      \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Krstulovic}},\ and\
      \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Nazarenko}},\ }\bibfield
      {title} {\bibinfo {title} {Direct and {Inverse} {Cascades} in {Turbulent}
      {Bose}-{Einstein} {Condensates}},\ }\href
      {https://doi.org/10.1103/PhysRevLett.130.133001} {\bibfield  {journal}
      {\bibinfo  {journal} {Phys. Rev. Letters}\ }\textbf {\bibinfo {volume}
      {130}},\ \bibinfo {pages} {133001} (\bibinfo {year} {2023})}\BibitemShut
      {NoStop}%
    \bibitem [{\citenamefont {Moffatt}(1969)}]{moffatt1969}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.~K.}\ \bibnamefont
      {Moffatt}},\ }\bibfield  {title} {\bibinfo {title} {The degree of knottedness
      of tangled vortex lines},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
      {journal} {J. Fluid Mech.}\ }\textbf {\bibinfo {volume} {36}},\ \bibinfo
      {pages} {7} (\bibinfo {year} {1969})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Biferale}\ \emph {et~al.}(2012)\citenamefont
      {Biferale}, \citenamefont {Musacchio},\ and\ \citenamefont
      {Toschi}}]{biferaleInverseEnergyCascade2012a}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
      {Biferale}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
      {Musacchio}},\ and\ \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
      {Toschi}},\ }\bibfield  {title} {\bibinfo {title} {Inverse energy cascade in
      three-dimensional isotropic turbulence},\ }\href@noop {} {\bibfield
      {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
      {volume} {108}},\ \bibinfo {pages} {164501} (\bibinfo {year}
      {2012})}\BibitemShut {NoStop}%
    \bibitem [{\citenamefont {Biferale}\ \emph {et~al.}(2013)\citenamefont
      {Biferale}, \citenamefont {Musacchio},\ and\ \citenamefont
      {Toschi}}]{biferale-etal-2013}%
      \BibitemOpen
      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
